---
title: "People Analytics [S2]"
author: "Ellaine Ho"
started: "2020-06-08"
output:
  html_document:
    df_print: paged
tl;dr: Demonstrating some basic R fluency.
---

## Breakout for Session 1 

1/ Create a Vector with values that run from 2 to 10.
```{r}
vector1 <- c(2:10)
vector1
```

2/ Create a Vector with values for the days in the week, starting from Monday and ending on Sunday.
```{r}
days_of_the_week <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday")
days_of_the_week
```

3/ Repeat 2 but this time have it list from Wednesday to Tuesday.
```{r}
days_of_the_week[3:2]
```

4/ Create a List with your (i) name, (ii) your birth month, (iii) your birth date, and (iv) your expected TC graudation year. 
```{r}
myinfo <- list("name"= "Ellaine", "birth_month" = 2, "birth_date" = 24, "grad_yr" = 2020)
myinfo
```

5/ Create a List with your (i) name and (ii) a Vector with all the degree-types (e.g., B.S., M.A., etc.) you expect by TC graduation.
```{r}
myinfo <- list("name" = "Ellaine", "degree" = "M.A.")
myinfo
```

Run this code!

```{r, results=FALSE}
# first create a set of vectors, these are the variables and values I want in this data frame
Emp_ID <- c("10101", "10032", "10224", "12005", "11010", "20200", "10042", "20104", "77023", "50034", 
            "11111", "98475", "33644", "33254", "66974", "21457", "99651", "20104", "88594", "21546")
Start_Date <- as.Date(c("2011-02-05", "2012-04-08", "2009-10-05", "2014-09-09", "2015-05-05", 
                        "2010-01-05", "2005-05-10", "2014-11-25", "2010-04-10", "2010-10-08",
                        "2012-05-05", "2010-04-10", "2011-10-30", "2014-09-04", "2014-12-05", 
                        "2014-05-07", "2005-05-10", "2014-11-25", "2015-12-05", "2010-10-08"))
Salary <- c(100200, 115000, 104000, 90000, 85000, 140000, 125500, 111000, 75000, 88000, 
            140200, 131000, 14000, 78000, 99400, 125000, 114400, 98000, 145000, 108000)
Annual_Bonus <- c(15000, 20000, 18000, 16500, 17800, 20000, 19000, 14000, 18000, 15000,
                  15500, 16000, 16000, 13600, 14400, 10000, 16500, 12500, 13500, 16000)
Retention_Bonus <- c(NA, NA, NA, 10000, NA, NA, NA, 10000, NA, NA,
                     20000, NA, NA, NA, 10000, NA, NA, 10000, NA, NA)

# this next line combines the different vectors and creates a data frame called "emp"
# note how I'm careful to include the 'stringAsFactors = FALSE' command

emp <- data.frame(Emp_ID, Start_Date, Salary, Annual_Bonus, Retention_Bonus, stringsAsFactors = FALSE)
emp  # run the dataframe I just created and see if it has the information I expect it to have
```

6/ Display the Employee ID of the most tenured employee (i.e., who has been at this company the longest?).
```{r}
most_tenured <- min(emp$Start_Date)
emp %>% select(Emp_ID) %>% filter(Start_Date == most_tenured)

```

7/ Do the same thing as #1, but use a different method (e.g., if you used numbers first, use column names, or vice-versa).
```{r}
# what does this mean?
```

8/ Display all the names of the columns in the dataframe.
```{r}
names(emp)
```
  
9/ Display the Employee ID of the person with the highest base salary.
```{r}
emp %>% select(Emp_ID) %>% filter(Salary == max(Salary))
```

10/ Display the entire vector of retention bonuses.
```{r}
emp$Retention_Bonus
```

11/ Display just the unique values of the retention bonuses.
```{r}
unique(emp$Retention_Bonus)
```

12/ Display just the second row of the data frame.
```{r}
emp[2, ]
```
   
13/ Display the count of the number of rows in the data frame.   
```{r}
 nrow(emp)
```
 